The \project{unRAVE} catalog

### 2016-08-31 article/unrave.tex
Minors

At the test step optimization we store the covariance matrix $\bm{\Sigma}$ for the labels
$\ell$, which provides us with the formal errors on $\ell$.  We judge the veracity of these
formal errors in our validation experiments in Section \ref{sec:validation}.

@@

% All them hax.

\section{Validation experiments}
\label{sec:validation}

Here we describe a

@@

% Identify outliers:
% --> Chi-sq of the sample.
% --> Convex hull? Distance to plane?
% --> Stars with morphological classification
% --> Some rogue gallery of a few high S/N cases that have clearly gone haywire?

@@

% External validation: 
% --> Gaia-ESO Survey
% --> APOGEE / EPIC (whichever was not used)
% --> Literature studies presented in Kordopatis+ 2014
% --> Gold standards (incl. exoplanet host star studies): Reddy (2003, 2006), Bensby (2014), Valenti & Fischer (2005)

>>>>

At the test step optimization we store the covariance matrix $\bm{\Sigma}$ for the labels
$\ell$, which provides us with the formal errors on $\ell$.  The formal errors are expected
to be underestimated, and in Section \ref{sec:validation} we judge the veracity of these 
errors through validation experiments.

@@

% All them hax used to combine all the results.

% --> Chi-sq of the sample.
% --> Convex hull? Distance to plane?

\section{Validation experiments}\label{sec:validation}

We have already performed leave-one-out cross-validation on all of our models
as part of the hyperparameter selection.  Here we describe the results from our
internal, external and astrophysical validation checks.

@@

% Identify outliers:
% --> Stars with morphological classification
% --> Some rogue gallery of a few high S/N cases that have clearly gone haywire?

@@

% External validation: 
% --> Gaia-ESO Survey
% --> Literature studies presented in Kordopatis+ 2014
% --> Gold standards (incl. exoplanet host star studies): Reddy (2003, 2006), Bensby (2014), Valenti & Fischer (2005)
